%*******************************************************
% Acknowledgments
%*******************************************************
\pdfbookmark[1]{Acknowledgements}{acknowledgements}

\bigskip

\begingroup
\let\clearpage\relax
\let\cleardoublepage\relax
\let\cleardoublepage\relax
\chapter*{Acknowledgements}

\def\thanks#1{%
\begingroup
\leftskip1em
\noindent #1
\par
\endgroup
}

I would like to thank all five members of my committee, starting with \textbf{Rolf Kipfer}, aka the real\textit{ RoKi Balboa}, \textbf{Matthias Brennwald}, \textbf{Mark Lever}, \textbf{Douglas Kip Solomon}, and \textbf{Maria Schönbächler}.
Two special thanks go to RoKi, who helped cool down my strong ibex mind and supported me at every stage of this thesis, and to Matthias, without whom no data collection would have been possible.
Both of them were instrumental in turning early drafts into what you see today.

I am also grateful to all past and present members of the Environmental Isotopes, Tracer Hydrogeology, and Environmental Microbiology groups at Eawag, University of Basel, and ETH Zürich, for their generous support in the field, the lab, and the office.
A special shout-out to \textbf{Yama Tomonaga}, always there in case of urgency, and the French squad --- \textbf{Capucine Marion}, \textbf{Stéphanie Musy}, and \textbf{Théo Blanc} --- as well as \textbf{Nora Bernet} and \textbf{David Haaf}, for making conferences and PhD life more enjoyable.
Their mental support and feedback was more than welcome.
A warm thank you to all colleagues who helped improve the chapters of this thesis with their generous advice and collaborative spirit. 

Thanks also to the W+T department, the Noble Gas Laboratory at ETH (aka “the cellar”), especially \textbf{Colin Maden}, \textbf{Andreas Süsli}, and \textbf{Werner Erni}, and the GDC Diversity Center at ETH -- \textbf{Aria Minder}, \textbf{Silvia Kobel}, and \textbf{Jean-Claude Walser} -- for their invaluable help in both laboratory work and field logistics.

I am very grateful to my collaborators at Alpgeo, especially \textbf{Eline Mignot}, \textbf{Gabriele Bianchetti}, and \textbf{Vincent Ferrier}; \textbf{Jean-Marie Rouiller} from Cesla; and \textbf{André Défago}, for enabling access to the thermal wells of Lavey-les-Bains and for their continued trust and collaboration.

Finally, to my family --- \textbf{Mueti}, \textbf{Chaly}, \textbf{Sév}, and \textbf{Sandy} --- my friends, and especially \textbf{Tilla}: thank you for your endless support and for helping me escape the sometimes harsh reality of PhD life.

\endgroup
